Type Refinements for the Working Class

### 2015-11-11 paper.tex
Add ambient LF section; use cool todonotes package

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{leftidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{url}

@@

\ifcolored
  \bigskip
  \begin{remark*}[Typographical Conventions]
    In this paper, we hint at the \emph{modes} of judgments and assertions
    \cite{harper:2016} using colors, marking inputs with
    $\IMode{\texttt{blue}}$ and outputs with $\OMode{\texttt{red}}$. As a rule
    of thumb, inputs are things which are supplied when checking the
    correctness of a judgment, and outputs are things which are synthesized in
    the process.
  \end{remark*}
\fi

@@

See \cite{sterling-morrison:2015} for the development of abstract binding trees
with symbols.

TODO: give a brief description of the framework, and present its rules.

@@

% TODO: define maps of refined contexts, then change weakening lemma to
% monotonicity, which is stronger and more useful.
\begin{thm}[Weakening]
  If $\Refines{\Phi}{\phi}{\tau}$, then $\Refines{\Phi,u:\psi}{\phi}{\tau}$ (supposing
  $\NotIn{u}{\Dom\Phi}$ and $\Refines{\Phi}{\psi}{\sigma}$).
\end{thm}
\begin{proof}
  This follows trivially from the rule $\RefinesCtxSnoc$ and the canonical renaming
  $\Upsilon\hookrightarrow\Upsilon,u:\sigma$.
\end{proof}

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{leftidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{url}
\usepackage{todonotes}

@@

@@

See \cite{sterling-morrison:2015} for the development of abstract binding trees
with symbols. \todo[inline]{give a brief description of the framework, and present its
rules.}

\section{The Ambient Logical Framework}

\ifcolored
  In this paper, we hint at the \emph{modes} of judgments and assertions
  \cite{harper:2016} using colors, marking inputs with
  $\IMode{\texttt{blue}}$ and outputs with $\OMode{\texttt{red}}$. As a rule
  of thumb, inputs are things which are supplied when checking the
  correctness of a judgment, and outputs are things which are synthesized in
  the process.
\fi

\todo[inline]{explain general and hypothetical judgment with respect to ABTs (probably
following Bob's book).}

@@

\todo[inline]{%
  define maps of refined contexts, then change weakening lemma to
  monotonicity, which is stronger and more useful.
}
\begin{thm}[Weakening]
  If $\Refines{\Phi}{\phi}{\tau}$, then $\Refines{\Phi,u:\psi}{\phi}{\tau}$ (supposing
  $\NotIn{u}{\Dom\Phi}$ and $\Refines{\Phi}{\psi}{\sigma}$).
\end{thm}
\begin{proof}
  This follows trivially from the rule $\RefinesCtxSnoc$ and the canonical renaming
  $\Upsilon\hookrightarrow\Upsilon,u:\sigma$.
\end{proof}
